\huge Tor's Usability for Censorship Circumvention

### 2016-04-14 pets2017-paper/pets2017-paper.tex
fill in some results.

\begin{figure}
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & & \\
public relays blocked & X & X & \\
default bridges blocked & X & X & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires participants to click ``Connect'';
E2 requires selection of an included bridge;
and E3 requires selection of a specific included bridge,
or manual configuration of a custom bridge.
E2's blocking is a superset of E1's;
similarly E3's is a superset of E2's.
}
\label{tab:environments}
\end{figure}

@@

\subsection{Results}

% This table is generated by info.R.
\begin{tabular}{l r r r r}
& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
\noalign{\hrule}
E1-NEW & 19/19 & 100\% & 0:20 \\
E1-OLD & 19/19 & 100\% & 1:01 \\
E2-NEW & 18/19 & 95\% & 3:22 \\
E2-OLD & 16/19 & 84\% & 4:01 \\
E3-NEW & 13/20 & 65\% & 12:38 \\
E3-OLD & 10/20 & 50\% & 18:16 \\
\end{tabular}

@@

\begin{figure}
\centering
\includegraphics{time_to_success_ecdf}

% Generated by info.R:
\begin{tabular}{l r r r r}
& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
\noalign{\hrule}
E1-NEW & 100\% & 100\% & 100\% & 100\% \\
E1-OLD & 58\% & 100\% & 100\% & 100\% \\
E2-NEW & 11\% & 79\% & 89\% & 95\% \\
E2-OLD & 16\% & 68\% & 79\% & 84\% \\
E3-NEW & 0\% & 25\% & 45\% & 65\% \\
E3-OLD & 0\% & 20\% & 25\% & 50\% \\
\end{tabular}

\caption{
Cumulative success rates over time.
We stopped participants after 40 minutes;
this graph shows what the success rate would have been
at different cutoff times.
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time.
After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.
}
\label{fig:time_to_success_ecdf}
\end{figure}

@@

{\color {red} 
What to talk about: 
\begin{itemize}
\item{Did the new interface improve the success rate?}
\item{Did the new interface help in only certain environments or certain people?}
\item{Did the new interface improve the time to success?}
\item{What are remaining issues?} 
\item{What people did while configuring the interface}
\item{Where people downloaded Tor browser if they did it themselves} 
\item{Xlab versus craigslist} 
\end{itemize}

Graph: 
\begin{itemize}
\item{success rate}
\item{time spent on each screen}
\item{order pluggable transports were chosen}
\item{transitions between windows for all participants}
\end{itemize} 
}

\section{Discussion} 
{\color {red} process the results, talking about the speculative here.}

@@

We took an approach that optimized for the average case user yet was conservative enough in automation to allow users to connect without leaking that they use Tor. Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success. We encourage future work to explore some of the non-conservative changes and alternate approaches that we were not able to test in these series of experiments.

On a fundamental level, there are alternative approaches to manual configuration. An alternative approach has the potential to be highly effective, but would warrant future research: \\

>>>>

\begin{table}
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & & \\
public relays blocked & X & X & \\
default bridges blocked & X & X & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires participants to click ``Connect'';
E2 requires selection of an included bridge;
and E3 requires selection of a specific included bridge,
or manual configuration of a custom bridge.
E2's blocking is a superset of E1's;
similarly E3's is a superset of E2's.
}
\label{tab:environments}
\end{table}

@@

\subsection{Results} 
Results from statistical analyses say: 
\begin{itemize} 
	\item{{\bfseries impact of censorship environment on success rate is not significant.} 
	Kruskal-Wallis, chi-squared = 4.7059, df = 2, p-value = 0.09509}
	\item{{\bfseries impact of censorship environment on time to completion is significant.} 
	Kruskal-Wallis, chi-squared = 64.565, df = 2, p-value = 9.547e-15}
	\item{{\bfseries impact of configuration version on success rate is not significant.}
	Mann-Whitney, W = 5.5, p-value = 0.8248}
	\item{{\bfseries impact of configuration interface on time to completion is not significant.} 
	Mann-Whitney, W = 991, p-value = 0.3197}
\end{itemize}

A logistic regression model showing effects of censorship environment, interface version,
and recruitment pool on success finds that a difficult censorship environment is the most
significant factor in a participant failing. Xlab participants were more likely to succeed. 
Participants with the old version of the interface were more likely to fail.

Coefficients:
             Estimate Std. Error z value Pr(>|z|)  
(Intercept)   19.4556  1684.3342   0.012   0.9908  
envE2        -17.3458  1684.3342  -0.010   0.9918  
envE3        -19.2652  1684.3341  -0.011   0.9909  
versionOLD    -0.7095     0.5793  -1.225   0.2206  
poolxlab       1.1218     0.5968   1.880   0.0601 .
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

A linear regression model showing effects of censorship environment, interface version, 
and recruitment pool on success finds that a difficult censorship environment is the most
significant factor in taking a long time to complete the task. Participants with the old version
of the interface and participants recruited from Xlab were likely to take longer.

Coefficients:
            Estimate Std. Error t value Pr(>|t|)    
(Intercept)   -42.79      86.70  -0.494  0.62280    
envE2         300.65      90.13   3.336  0.00124 ** 
envE3         923.66     100.94   9.150 1.68e-14 ***
versionOLD    104.78      78.70   1.331  0.18642    
poolxlab       92.41      78.88   1.172  0.24445    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\
	E1-OLD & 19/19 & 100\% & 1:01 \\
	E2-NEW & 18/19 & 95\% & 3:22 \\
	E2-OLD & 16/19 & 84\% & 4:01 \\
	E3-NEW & 13/20 & 65\% & 12:38 \\
	E3-OLD & 10/20 & 50\% & 18:16 \\
	\end{tabular}
\caption{A summary of partipants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were not used to calculate the median time
to success.}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{time_to_success_ecdf}
\caption{
Cumulative success rates over time, by censorship environment and interface.
We stopped participants after 40 minutes. Those who did not finish were assigned
an arbitrarily high number greater than 40 minutes. 
}
\label{fig:time_to_success_ecdf}
\end{figure}

\begin{table}
\centering 
	% Generated by info.R:
	\begin{tabular}{l r r r r}
	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
	\noalign{\hrule}
	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
	\end{tabular}
\caption{This Table shows what the success rate would have been
at different cutoff times.
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time.
After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.}
\end{table}

@@

\begin{figure} 
%\includegraphics{}
{\color {red} TODO} 
\caption{time spent on each screen}
\end{figure}

\begin{figure} 
%\includegraphics{}
{\color {red} TODO} 
\caption{order pluggable transports were chosen}
\end{figure}

\section{Discussion} 
{\color {red} TODO: improvements.} \\
{\color {red} TODO: subjective observations.} \\
{\color {red} TODO: remaining issues.} \\
{\color {red} recommendations are below.} \\

{\color {red} Speculation of why certain things happened--long progress bar (there was no feedback so people assumed that they had to wait), transport selections (people in the new interface didn't see the advice sometimes), etc.}

@@

We took an approach that optimized for the average case user yet was conservative enough in automation to allow users to connect without leaking that they use Tor. Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success. We encourage future work to explore some of the non-conservative changes and alternate approaches that we were not able to test in these series of experiments.\\
